\textbf{International Transport costs:\\New Findings from modeling additive costs}\\Online Appendix (Not for Publication)

### 2022-03-11 redaction/JEGeo/revision_JEGeo/revised_article/DHP_JoEG_accepted_version.tex
Ajour remerciements référés-éditeur

\title{\textsc{International Transport costs:\\New Findings from modeling additive costs}\thanks{%We thank the referees, as well as the editor, William Kerr, for insightful comments, which helped to significantly improve the paper.
We are grateful to Holger G\"{o}rg, S\'{e}bastien Jean and Vincent Vicard for their critics and suggestions on earlier drafts. The paper has also greatly benefited from remarks from the participants at ETSG 17\textsuperscript{th} (Helsinki), DEGIT XXII (Paris), seminars at the universities of California-Irvine, Paris-Dauphine, Paris-I and Nancy and the Kiel Institute for the World Economy. Any remaining errors are ours. This paper was partly funded by a university grant from the University of Lille. It features an online appendix containing additional results, available on the authors' websites%and on \url{https://github.com/gdaudin/trade_costs}
.}}

>>>>

\title{\textsc{International Transport costs:\\New Findings from modeling additive costs}\thanks{We warmly thank the referees, as well as the editor, William Kerr, for insightful comments, which helped to significantly improve the paper.
We are grateful to Holger G\"{o}rg, S\'{e}bastien Jean and Vincent Vicard for their critics and suggestions on earlier drafts. The paper has also greatly benefited from remarks from the participants at ETSG 17\textsuperscript{th} (Helsinki), DEGIT XXII (Paris), seminars at the universities of California-Irvine, Paris-Dauphine, Paris-I and Nancy and the Kiel Institute for the World Economy. Any remaining errors are ours. This paper was partly funded by a university grant from the University of Lille. It features an online appendix containing additional results, available on the authors' websites%and on \url{https://github.com/gdaudin/trade_costs}
.}}
